### 2021-04-22 input/abstract.tex
wip intro, minor fix in other sections

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
\TODO{weird}
  every \process only indexes its closest replica, and
  connected \processes with similar index compose a partition. Our
  decentralized implementation \NAME
  \begin{inparaenum}[(i)]
  \item is efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time,
  especially in dynamic \TODO{weird, we do not really test dynamic}
Edge infrastructures. As such, \NAME can
  constitute the building block of new geo-distributed services.
\end{abstract}

>>>>

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
\TODO{weird}
  every \process only indexes its closest replica, and
  connected \processes with similar index compose a partition. Our
  decentralized implementation \NAME
  \begin{inparaenum}[(i)]
  \item is efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time. As
  such, \NAME can constitute the building block of new geo-distributed
  services.
\end{abstract}

\begin{IEEEkeywords}
Edge infrastructures, decentralized content indexing, scoped
broadcast, logical partitioning protocol
\end{IEEEkeywords}

### 2021-04-22 input/background.tex
wip intro, minor fix in other sections

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other processes of its new content. \Process~$R$
can use uniform reliable broadcast~\REF and epidemic propagation~\REF
to guarantee that
\begin{inparaenum}[(i)]
\item every process eventually knows the content location
\item efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

@@

Every \process ends up with at least 1 known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
\processes to communicate with based on metrics~\REF, \processes in
our context have no control over their neighboring processes.

@@

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belong to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partition would block the
propagation of other partitions.
\end{asparadesc}

>>>>

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new content. \Process~$R$
can use uniform reliable broadcast~\REF and epidemic propagation~\REF
to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

@@

Every \process ends up with at least 1 known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
\processes to communicate with based on metrics~\REF, \processes in
our context have no control over their neighboring \processes.

@@

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belong to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partition would block the
propagation of other partitions.
\end{asparadesc}

### 2021-04-22 input/introduction.tex
fix refs
wip intro, minor fix in other sections

There is an ongoing evolution of storing data from the cloud to the
edges of the network. Either because it is where it has been created
and it is too expensive to be transmitted through the network, or
because it has been replicated to bring data closer to the end users
~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, the design and the development of building
blocks to manage data sets across Edge infrastructures have been
investigated for the last few years \cite{confais2017performance,
  confais2017object, fogstore, hasenburg2020towards}.  Although these
systems, provide good properties such as favouring network traffic
confinement by writting data locally and replicating contents
according to the effective needs, determining the location where to
get the content might be more expensive than retrieving the content
itself.
%
Indeed, those systems, when not using a centralized index stored in a
Cloud, rely on a Distributed Hash Table (DHT) across the different
nodes composing the infrastructure: When a client wants to access a
specific content, it has to perform a request to a remote process to
determine from which node(s) it will retrieve the content.  Once it has
retrieved the content, a local replica
is created to improve the performance for future accesses and the
process in charge of maintaining the index is contacted once again to reflect this
new location.
%

@@

Such a protocol contradicts with the objective of Edge
infrastructures that aims at reducing the impact of the
latency as well as the volume of data passing through the network:
\begin{itemize}
  \item In addition to hot spot and partitioning issues, accessing a
    remote node to find the location(s) of a content incurs an
    additional delay~\cite{asrese2019measuring, doan2019tracing} to
    get the object, before being able to start its downloading.
  \item There is no information to select the ``best'' node among the
     possible candidates from which the content  could be
     retrieved. In most cases, this results in parallel requests performed by the client node to
     each candidate with the goal of retrieving the content as efficient
     as possible.
\end{itemize}

@@

The rest of this paper is organized as
follows. Section~\ref{sec:background} introduces background, and
details the motivation behind our proposal.
Section~\ref{sec:adapative} describes the protocol behavior, as well
as the formal definition of the underlying
algorithms. Section~\ref{sec:experimentation} presents the Peersim
evaluations.  Related work is discussed in
Section~\ref{sec:related_work} and finally
Section~\ref{sec:conclusion} concludes this article and highlights a
few future works.

>>>>

\input{input/figpartitionintuition.tex} %% positioning

In recent years, the data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This shift aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud~\REF, rely on distributed hash
tables~\cite{maymounkov2002kademlia} spread across the different
\processes composing the infrastructure. When a client wants to access
specific content, it requests a remote \process to provide at least
one \process identity to retrieve this content from. After it
retrieved the content, the client can create another replica to
improve the performance of future accesses, but it must contact the
content indexing service again to notify of such change.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

These approaches directly contradict with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays that occur even before the actual download
started~\cite{asrese2019measuring, doan2019tracing}.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer~\REF. In turns, either a client wastes
network resources, or faces lower response time.
%% there is no information to select the ``best'' node among the possible
%% candidates from which the content could be retrieved. In most cases,
%% this results in parallel requests performed by the client node to each
%% candidate with the goal of retrieving the content as efficient as
%% possible.

@@

The rest of this paper is organized as
follows. Section~\ref{sec:background} introduces background, and
details the motivation behind our proposal.
Section~\ref{sec:adaptive} describes the protocol behavior, as well
as the formal definition of the underlying
algorithms. Section~\ref{sec:experimentation} presents the Peersim
evaluations.  Related work is discussed in
Section~\ref{sec:related_work} and finally
Section~\ref{sec:conclusion} concludes this article and highlights a
few future works.
